Measuring security performance in the Android ecosystem

### 2015-06-03 dastats.tex
./update.sh (plus some manual forward porting)

\newcommand{\daEndDate}{2015-05-21}

@@

\newcommand{\daNumManufacturers}{298}

@@

\newcommand{\daNumModels}{2\,690}

@@

\newcommand{\daNumSigOperators}{14}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{0.551}

@@

\newcommand{\daSecurityScoreNominal}{2.83}
\newcommand{\daSecurityScore}{$2.83 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{87.0\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$87.0 \pm 4.9\%$}

@@

\newcommand{\daCurrentMeanInsecurityPercTwosf}{$87 \pm 4\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{13.0\%}
\newcommand{\daCurrentMeanSecurityPerc}{$13.0 \pm 4.9\%$}

@@

\newcommand{\daCurrentMeanSecurityPercTwosf}{$13 \pm 4\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.13}
\newcommand{\daCurrentVulnFree}{$0.13 \pm 4.92$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{0.213}
\newcommand{\daCurrentUpdatednessNominal}{0.0327}
\newcommand{\daCurrentUpdatedness}{$0.0327 \pm 0.0006$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.27\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.27 \pm 0.06\%$}

@@

\newcommand{\daDailyParticipationNominal}{906}
\newcommand{\daDailyParticipation}{$906 \pm 224$}

@@

\newcommand{\daNumOSVersionUpdates}{3\,830}

@@

\newcommand{\daOSCurveFitParamFirst}{84.9}

@@

\newcommand{\daOSCurveFullDeployed}{$1\,120 \pm 255\,000$}

@@

\newcommand{\daAPICurvePolyRMSE}{0.114}
\newcommand{\daAPICurveSplineRMSE}{0.114}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.933}
\newcommand{\daAPICurveHalfDeployedYears}{$0.933 \pm 0.243$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.32 \pm 0.00$ & 0.64 & $3.83 \pm 0.01$ \\  Motorola & $0.17 \pm 0.00$ & $0.12 \pm 0.00$ & 0.73 & $3.03 \pm 0.01$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & 0.63 & $2.71 \pm 0.00$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & 1.09 & $2.61 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & 0.89 & $2.58 \pm 0.00$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & 6.01 & $2.31 \pm 0.02$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & 1.04 & $1.94 \pm 0.00$ \\  Symphony & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 5.00 & $0.27 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 5.97 & $0.24 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.83}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.83 \pm 0.01$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{129}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.236}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.236 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & 1.53 & $4.74 \pm 0.03$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & 6.06 & $3.59 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & 5.92 & $3.18 \pm 0.04$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & 0.55 & $2.97 \pm 0.00$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & 0.39 & $2.91 \pm 0.01$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & 1.59 & $2.42 \pm 0.02$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & 1.23 & $2.28 \pm 0.01$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & 1.00 & $1.75 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & 2.52 & $1.43 \pm 0.02$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & 1.79 & $0.90 \pm 0.02$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & 6.25 & $0.59 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & 6.82 & $0.44 \pm 0.01$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 3.05 & $0.27 \pm 0.02$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & 6.91 & $0.25 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & 11.00 & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.74}
\newcommand{\daSecScoreBestmodelScore}{$4.74 \pm 0.02$}

@@

\newcommand{\daSecScoreWorstmodelScoreNominal}{0.0001}
\newcommand{\daSecScoreWorstmodelScore}{$0.0001 \pm 0.0276$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.38 \pm 0.00$ & $0.48 \pm 0.00$ & 0.59 & $5.08 \pm 0.01$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & 0.55 & $2.66 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table}}
\newcommand{\daTabSecScoresoperator}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & 0.37 & $3.84 \pm 0.01$ \\  T-Mobile & $0.20 \pm 0.00$ & $0.18 \pm 0.00$ & 0.42 & $3.73 \pm 0.01$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & 0.39 & $3.52 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & 0.40 & $3.46 \pm 0.01$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.52 & $3.23 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & 0.50 & $3.18 \pm 0.01$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & 0.43 & $3.09 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & 0.82 & $2.83 \pm 0.01$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & 0.87 & $2.80 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & 1.25 & $1.81 \pm 0.01$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & 1.62 & $1.27 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.07 \pm 0.00$ & 2.08 & $0.88 \pm 0.01$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.05 \pm 0.00$ & 2.03 & $0.85 \pm 0.00$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & 2.62 & $0.53 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.84}
\newcommand{\daSecScoreBestoperatorScore}{$3.84 \pm 0.01$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{95}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.531}
\newcommand{\daSecScoreWorstoperatorScore}{$0.531 \pm 0.005$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{72}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.143 & 0.0 \\weight $u$ & 0.444 & 0.133 & 0.214 & 0.0 \\$f$ & 0.444 & 0.733 & 0.429 & 0.0 \\$m$ & 0.667 & 0.733 & 0.357 & 0.5 \\$u$ & 0.889 & 0.667 & 0.714 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.91 \pm 2.21$ & $-0.666 \pm 2.5$ & $-3.27 \pm 1.38$ & $-3.35 \pm 1.84$ \\weight $m$ & $-0.295 \pm 0.273$ & $-0.102 \pm 0.314$ & $-0.458 \pm 0.176$ & $-0.485 \pm 0.209$ \\equal & $-0.116 \pm 0.065$ & $-0.0391 \pm 0.112$ & $-0.146 \pm 0.048$ & $-0.166 \pm 0.028$ \\weight $u$ & $-0.0522 \pm 0.127$ & $-0.0154 \pm 0.239$ & $0.0199 \pm 0.0787$ & $-0.0137 \pm 0.127$ \\$u$ & $0.518 \pm 1.6$ & $0.198 \pm 2.14$ & $1.51 \pm 0.95$ & $1.36 \pm 1.52$ \\$f$ & $1.04 \pm 0.58$ & $0.351 \pm 1.01$ & $1.31 \pm 0.44$ & $1.5 \pm 0.2$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.954}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.954 \pm 0.473$}

@@

\newcommand{\daGPAPICurveHalfDeployed}{$348 \pm 173$}

@@

\newcommand{\daGPAPIPerAPIMeanNominal}{0.00453}
\newcommand{\daGPAPIPerAPIMean}{$0.00453 \pm 0.00343$}
\newcommand{\daGPAPIPerAPIStdevNominal}{0.0211}
\newcommand{\daGPAPIPerAPIStdev}{$0.0211 \pm 0.0127$}
\newcommand{\daGPAPIPerAPIAbsMeanNominal}{0.0144}
\newcommand{\daGPAPIPerAPIAbsMean}{$0.0144 \pm 0.0066$}

@@

\newcommand{\daGPAPIPerAPIParametersTable}{\begin{table} \centering \begin{tabular}{c|S|S} API Version & ${t_0}$ & $\mathrm{decay}$ \\ \hline2	&	0.0	&	0.0237\\3	&	0.0	&	0.0235\\4	&	0.0	&	0.00689\\5	&	59.1	&	0.00465\\6	&	0.0	&	0.0043\\7	&	0.0	&	0.00499\\8	&	47.7	&	0.00415\\9	&	155	&	0.00365\\10	&	90.2	&	0.00364\\11	&	432	&	0.00228\\12	&	355	&	0.00228\\13	&	304	&	0.00236\\14	&	218	&	0.00239\\15	&	160	&	0.00239\\16	&	142	&	0.00227\\17	&	288	&	0.00195\\18	&	119	&	0.00141\\19	&	119	&	0.00153\\\end{tabular} \caption{Parameters for different API versions} \label{tab:per_api_parameters} \end{table}}

@@

\newcommand{\daGPAPISeventeenLaterProportion}{72.4\%}
\newcommand{\daGPAPISeventeenEarlierProportion}{27.6\%}

@@

\newcommand{\daGPAPISeventeenFullDeployment}{2017-10-29}
\newcommand{\daGPAPISeventeenCurveFitParamFirst}{288}

@@

\newcommand{\daGPAPISeventeenCurveFitRMSE}{0.0272}
\newcommand{\daGPAPISeventeenCurvePolyRMSE}{0.00888}
\newcommand{\daGPAPISeventeenCurveSplineRMSE}{0.00888}
\newcommand{\daGPAPISeventeenCurveHalfDeployedYearsNominal}{1.77}
\newcommand{\daGPAPISeventeenCurveHalfDeployedYears}{$1.77 \pm 0.07$}
\newcommand{\daGPAPISeventeenCurveHalfDeployedNominal}{644}
\newcommand{\daGPAPISeventeenCurveHalfDeployed}{$644 \pm 28$}
\newcommand{\daGPAPISeventeenCurveFullDeployedYearsNominal}{5.01}
\newcommand{\daGPAPISeventeenCurveFullDeployedYears}{$5.01 \pm 1.11$}
\newcommand{\daGPAPISeventeenCurveFullDeployedNominal}{1\,830}
\newcommand{\daGPAPISeventeenCurveFullDeployed}{$1\,830 \pm 404$}

@@

\newcommand{\daMonthsDevices}{1\,780}

@@

>>>>

\newcommand{\daEndDate}{2015-05-26}

@@

\newcommand{\daNumManufacturers}{299}

@@

\newcommand{\daNumModels}{2\,700}

@@

\newcommand{\daNumSigOperators}{15}

@@

\newcommand{\daMeanOutstandingVulnerabilities}{$0.771 \pm 2.66e$}

@@

\newcommand{\daSecurityScoreNominal}{2.53}
\newcommand{\daSecurityScore}{$2.53 \pm 0.00$}
\newcommand{\daCurrentMeanInsecurityPercNominal}{87.1\%}
\newcommand{\daCurrentMeanInsecurityPerc}{$87.1 \pm 0.1\%$}

@@

\newcommand{\daCurrentMeanInsecurityPercTwosf}{$87 \pm 0\%$}
\newcommand{\daCurrentMeanSecurityPercNominal}{12.9\%}
\newcommand{\daCurrentMeanSecurityPerc}{$12.9 \pm 0.1\%$}

@@

\newcommand{\daCurrentMeanSecurityPercTwosf}{$13 \pm 0\%$}
\newcommand{\daCurrentVulnFreeNominal}{0.129}
\newcommand{\daCurrentVulnFree}{$0.129 \pm 0.001$}
\newcommand{\daCurrentMeanOutstandingVulnerabilities}{$0.209 \pm 9.49e$}
\newcommand{\daCurrentUpdatednessNominal}{0.0329}
\newcommand{\daCurrentUpdatedness}{$0.0329 \pm 0.0008$}
\newcommand{\daCurrentUpdatednessPercNominal}{3.29\%}
\newcommand{\daCurrentUpdatednessPerc}{$3.29 \pm 0.08\%$}

@@

\newcommand{\daDailyParticipationNominal}{903}
\newcommand{\daDailyParticipation}{$903 \pm 229$}

@@

\newcommand{\daNumOSVersionUpdates}{3\,840}

@@

\newcommand{\daOSCurveFitParamFirst}{85.0}

@@

\newcommand{\daOSCurveFullDeployed}{$1\,120 \pm 256\,000$}

@@

\newcommand{\daAPICurvePolyRMSE}{0.113}
\newcommand{\daAPICurveSplineRMSE}{0.113}
\newcommand{\daAPICurveHalfDeployedYearsNominal}{0.934}
\newcommand{\daAPICurveHalfDeployedYears}{$0.934 \pm 0.242$}

@@

\newcommand{\daTabSecScoresmanufacturer}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline LG & $0.20 \pm 0.00$ & $0.32 \pm 0.00$ & $0.88 \pm 0.00$ & $3.51 \pm 0.01$ \\  Motorola & $0.17 \pm 0.00$ & $0.12 \pm 0.00$ & $1.10 \pm 0.01$ & $2.57 \pm 0.01$ \\  Samsung & $0.13 \pm 0.00$ & $0.04 \pm 0.00$ & $0.88 \pm 0.00$ & $2.39 \pm 0.00$ \\  asus & $0.19 \pm 0.00$ & $0.52 \pm 0.01$ & $21.42 \pm 0.09$ & $2.30 \pm 0.02$ \\  Sony & $0.13 \pm 0.00$ & $0.19 \pm 0.00$ & $1.68 \pm 0.01$ & $2.04 \pm 0.01$ \\  HTC & $0.14 \pm 0.00$ & $0.09 \pm 0.00$ & $1.40 \pm 0.00$ & $2.02 \pm 0.01$ \\  other & $0.06 \pm 0.00$ & $0.04 \pm 0.00$ & $1.77 \pm 0.00$ & $1.25 \pm 0.00$ \\  Symphony & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $15.00 \pm 0.03$ & $0.24 \pm 0.01$ \\  walton & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $20.79 \pm 0.06$ & $0.23 \pm 0.01$ \\ \end{tabular} \caption{Security scores for manufacturers} \label{tab:sec_manufacturer} \end{table*}}

@@

\newcommand{\daSecScoreBestmanufacturerScoreNominal}{3.51}
\newcommand{\daSecScoreBestmanufacturerScore}{$3.51 \pm 0.01$}
\newcommand{\daSecScoreBestmanufacturerNumFullVersions}{130}

@@

\newcommand{\daSecScoreWorstmanufacturerScoreNominal}{0.235}
\newcommand{\daSecScoreWorstmanufacturerScore}{$0.235 \pm 0.007$}

@@

\newcommand{\daTabSecScoresmodel}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline Galaxy Nexus & $0.51 \pm 0.00$ & $0.55 \pm 0.01$ & $2.18 \pm 0.02$ & $4.29 \pm 0.03$ \\  Nexus 4 & $0.28 \pm 0.00$ & $0.82 \pm 0.01$ & $21.70 \pm 0.12$ & $3.58 \pm 0.04$ \\  Nexus 7 & $0.24 \pm 0.00$ & $0.74 \pm 0.01$ & $20.68 \pm 0.11$ & $3.16 \pm 0.04$ \\  Desire HD & $0.08 \pm 0.00$ & $0.05 \pm 0.00$ & $0.47 \pm 0.01$ & $2.78 \pm 0.02$ \\  other & $0.09 \pm 0.00$ & $0.14 \pm 0.00$ & $0.77 \pm 0.00$ & $2.68 \pm 0.00$ \\  HTC Sensation & $0.35 \pm 0.00$ & $0.01 \pm 0.01$ & $2.44 \pm 0.03$ & $1.88 \pm 0.03$ \\  HTC Desire S & $0.02 \pm 0.00$ & $0.02 \pm 0.00$ & $1.00 \pm 0.02$ & $1.75 \pm 0.03$ \\  GT-I9100 & $0.22 \pm 0.00$ & $0.02 \pm 0.00$ & $2.08 \pm 0.01$ & $1.59 \pm 0.01$ \\  GT-N7000 & $0.25 \pm 0.00$ & $0.00 \pm 0.00$ & $4.70 \pm 0.03$ & $1.04 \pm 0.02$ \\  GT-I9300 & $0.13 \pm 0.00$ & $0.01 \pm 0.00$ & $23.21 \pm 0.04$ & $0.57 \pm 0.01$ \\  GT-I9505 & $0.01 \pm 0.00$ & $0.13 \pm 0.00$ & $26.96 \pm 0.08$ & $0.43 \pm 0.01$ \\  GT-P1000 & $0.01 \pm 0.00$ & $0.00 \pm 0.01$ & $3.17 \pm 0.03$ & $0.28 \pm 0.02$ \\  GT-N7100 & $0.06 \pm 0.00$ & $0.00 \pm 0.01$ & $27.81 \pm 0.11$ & $0.24 \pm 0.02$ \\  HTC Desire HD & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $6.23 \pm 0.03$ & $0.01 \pm 0.02$ \\  Symphony W68 & $0.00 \pm 0.00$ & $0.00 \pm 0.01$ & $66.00 \pm 0.19$ & $0.00 \pm 0.03$ \\ \end{tabular} \caption{Security scores for models} \label{tab:sec_model} \end{table*}}

@@

\newcommand{\daSecScoreBestmodelScoreNominal}{4.29}
\newcommand{\daSecScoreBestmodelScore}{$4.29 \pm 0.02$}

@@

\newcommand{\daSecScoreWorstmodelScoreNominal}{1.3e-28}
\newcommand{\daSecScoreWorstmodelScore}{$1.3e-28 \pm 0.0276$}

@@

\newcommand{\daTabSecScoressummary}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline nexus & $0.37 \pm 0.00$ & $0.47 \pm 0.00$ & $0.82 \pm 0.00$ & $4.75 \pm 0.01$ \\  notnexus & $0.10 \pm 0.00$ & $0.02 \pm 0.00$ & $0.77 \pm 0.00$ & $2.37 \pm 0.00$ \\ \end{tabular} \caption{Security scores for nexus} \label{tab:sec_summary} \end{table*}}
\newcommand{\daTabSecScoresoperator}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} Name & $f$ & $u$ & $m$ & \textbf{score} \\ &&&& (out of 10) \\ \hline O2 uk & $0.26 \pm 0.00$ & $0.12 \pm 0.00$ & $0.51 \pm 0.01$ & $3.65 \pm 0.02$ \\  T-Mobile & $0.21 \pm 0.00$ & $0.18 \pm 0.00$ & $0.54 \pm 0.01$ & $3.56 \pm 0.02$ \\  Orange & $0.21 \pm 0.00$ & $0.09 \pm 0.00$ & $0.48 \pm 0.01$ & $3.39 \pm 0.02$ \\  Sprint & $0.18 \pm 0.00$ & $0.11 \pm 0.00$ & $0.51 \pm 0.01$ & $3.31 \pm 0.02$ \\  3 & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $0.70 \pm 0.01$ & $2.99 \pm 0.02$ \\  AT\&T & $0.12 \pm 0.00$ & $0.08 \pm 0.00$ & $0.54 \pm 0.01$ & $2.94 \pm 0.01$ \\  Vodafone uk & $0.13 \pm 0.00$ & $0.13 \pm 0.00$ & $0.73 \pm 0.01$ & $2.88 \pm 0.02$ \\  unknown & $0.11 \pm 0.00$ & $0.20 \pm 0.00$ & $1.22 \pm 0.00$ & $2.40 \pm 0.01$ \\  Verizon & $0.18 \pm 0.00$ & $0.09 \pm 0.00$ & $1.27 \pm 0.01$ & $2.30 \pm 0.01$ \\  n Telenor & $0.03 \pm 0.00$ & $0.12 \pm 0.00$ & $1.86 \pm 0.00$ & $1.29 \pm 0.01$ \\  Airtel & $0.05 \pm 0.00$ & $0.03 \pm 0.00$ & $2.42 \pm 0.00$ & $0.77 \pm 0.01$ \\  Robi & $0.00 \pm 0.00$ & $0.08 \pm 0.00$ & $3.26 \pm 0.02$ & $0.46 \pm 0.01$ \\  Grameenphone & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $3.09 \pm 0.00$ & $0.41 \pm 0.00$ \\  banglalink & $0.00 \pm 0.00$ & $0.04 \pm 0.00$ & $4.83 \pm 0.01$ & $0.17 \pm 0.01$ \\ \end{tabular} \caption{Security scores for operators} \label{tab:sec_operator} \end{table*}}

@@

\newcommand{\daSecScoreBestoperatorScoreNominal}{3.65}
\newcommand{\daSecScoreBestoperatorScore}{$3.65 \pm 0.01$}
\newcommand{\daSecScoreBestoperatorNumFullVersions}{97}

@@

\newcommand{\daSecScoreWorstoperatorScoreNominal}{0.172}
\newcommand{\daSecScoreWorstoperatorScore}{$0.172 \pm 0.005$}
\newcommand{\daSecScoreWorstoperatorNumFullVersions}{73}
\newcommand{\daTabDLDistances}{\begin{table} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline equal & 0.0 & 0.0667 & 0.0714 & 0.0 \\weight $m$ & 0.222 & 0.333 & 0.0714 & 0.0 \\weight $u$ & 0.222 & 0.133 & 0.0714 & 0.0 \\$f$ & 0.444 & 0.733 & 0.5 & 0.0 \\$m$ & 0.556 & 0.8 & 0.429 & 0.5 \\$u$ & 0.889 & 0.6 & 0.786 & 0.0 \\\end{tabular} \caption{Normalised Damerau-Levenshtein distances for different metrics} \label{tab:dl_distances} \end{table}}
\newcommand{\daTabChangeInScores}{\begin{table*} \centering \begin{tabular}{l|c|c|c|c} & manufacturer & model & operator & summary \\ \hline $m$ & $-1.13 \pm 1.77$ & $-0.133 \pm 2.4$ & $-2.51 \pm 1.66$ & $-2.67 \pm 1.83$ \\weight $m$ & $-0.184 \pm 0.21$ & $-0.0255 \pm 0.313$ & $-0.35 \pm 0.21$ & $-0.387 \pm 0.209$ \\equal & $-0.0792 \pm 0.0477$ & $-0.0136 \pm 0.122$ & $-0.11 \pm 0.05$ & $-0.133 \pm 0.028$ \\weight $u$ & $-0.053 \pm 0.127$ & $-0.0154 \pm 0.239$ & $0.0196 \pm 0.0792$ & $-0.0124 \pm 0.125$ \\$u$ & $0.182 \pm 1.42$ & $-0.0309 \pm 2.03$ & $1.19 \pm 1.08$ & $1.07 \pm 1.5$ \\$f$ & $0.713 \pm 0.43$ & $0.123 \pm 1.1$ & $0.991 \pm 0.536$ & $1.2 \pm 0.2$ \\\end{tabular} \caption{Mean change in scores for different metrics} \label{tab:change_in_scores} \end{table*}}

@@

\newcommand{\daGPAPICurveHalfDeployedYearsNominal}{0.953}
\newcommand{\daGPAPICurveHalfDeployedYears}{$0.953 \pm 0.472$}

@@

\newcommand{\daGPAPICurveHalfDeployed}{$348 \pm 172$}

@@

\newcommand{\daGPAPIPerAPIMeanNominal}{0.00459}
\newcommand{\daGPAPIPerAPIMean}{$0.00459 \pm 0.00346$}
\newcommand{\daGPAPIPerAPIStdevNominal}{0.0212}
\newcommand{\daGPAPIPerAPIStdev}{$0.0212 \pm 0.0127$}
\newcommand{\daGPAPIPerAPIAbsMeanNominal}{0.0145}
\newcommand{\daGPAPIPerAPIAbsMean}{$0.0145 \pm 0.0066$}

@@

\newcommand{\daGPAPIPerAPIParametersTable}{\begin{table} \centering \begin{tabular}{c|S|S} API Version & ${t_0}$ & $\mathrm{decay}$ \\ \hline2	&	0.0	&	0.0237\\3	&	0.0	&	0.0235\\4	&	0.0	&	0.00689\\5	&	59.1	&	0.00465\\6	&	2.4	&	0.00434\\7	&	0.0	&	0.00499\\8	&	47.7	&	0.00415\\9	&	155	&	0.00365\\10	&	90.2	&	0.00364\\11	&	432	&	0.00228\\12	&	356	&	0.00228\\13	&	304	&	0.00236\\14	&	219	&	0.00239\\15	&	160	&	0.0024\\16	&	142	&	0.00227\\17	&	289	&	0.00195\\18	&	120	&	0.00142\\19	&	120	&	0.00154\\\end{tabular} \caption{Parameters for different API versions} \label{tab:per_api_parameters} \end{table}}

@@

\newcommand{\daGPAPISeventeenLaterProportion}{73.1\%}
\newcommand{\daGPAPISeventeenEarlierProportion}{26.9\%}

@@

\newcommand{\daGPAPISeventeenFullDeployment}{2017-10-24}
\newcommand{\daGPAPISeventeenCurveFitParamFirst}{289}

@@

\newcommand{\daGPAPISeventeenCurveFitRMSE}{0.0275}
\newcommand{\daGPAPISeventeenCurvePolyRMSE}{0.0088}
\newcommand{\daGPAPISeventeenCurveSplineRMSE}{0.0088}
\newcommand{\daGPAPISeventeenCurveHalfDeployedYearsNominal}{1.76}
\newcommand{\daGPAPISeventeenCurveHalfDeployedYears}{$1.76 \pm 0.07$}
\newcommand{\daGPAPISeventeenCurveHalfDeployedNominal}{643}
\newcommand{\daGPAPISeventeenCurveHalfDeployed}{$643 \pm 28$}
\newcommand{\daGPAPISeventeenCurveFullDeployedYearsNominal}{4.99}
\newcommand{\daGPAPISeventeenCurveFullDeployedYears}{$4.99 \pm 1.12$}
\newcommand{\daGPAPISeventeenCurveFullDeployedNominal}{1\,820}
\newcommand{\daGPAPISeventeenCurveFullDeployed}{$1\,820 \pm 408$}

@@

\newcommand{\daMonthsDevices}{1\,790}

@@

\newcommand{\daAPISeventeenReleaseDateMonth}{October 2012}
\newcommand{\daGPAPISeventeenFullDeploymentMonth}{October 2017}
\newcommand{\daMeanOutstandingVulnerabilitiesNominal}{0.771}
\newcommand{\daCurrentMeanOutstandingVulnerabilitiesNominal}{0.209}
\newcommand{\daModelHalfDeployment}{27}
\newcommand{\daModelFullDeployment}{316}
\newcommand{\daModelHalfDeploymentYears}{0.074}
\newcommand{\daModelFullDeploymentYears}{0.866}
\newcommand{\daMeanOutstandingProbability}{1\%}
\newcommand{\daMeanOutstandingUncertaintyEquation}{$0.99^n$}
